---
title: "Plot accidents on a map"
author: "Rafal Glabski"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Plot accidents on a map}
  %\VignetteEngine{knitr::knitr}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package aims at easy processing of FARS data files. Let's scan through it's funcitons. But first, let's set the working directory to the directory with FARS data files. 

```{r set working directory}
require(fars.pack)
old_path <- getwd()
file_path <- system.file("extdata", package = "fars.pack")
dir(file_path)
```

There are 3 data files attached with this package. They consists of data from 2013 to 2015. Let's read one of the files with `fars_read` function.

```{r read}
setwd(file_path)
fars2015 <- fars_read(dir()[3])
head(fars2015)
```

The output tibble has 52 columns describing accidents. We can plot accidents on a map for a selected state. The function `fars_map_state` does that.

```{r plot}
setwd(file_path)
# state number 1
fars_map_state(1, 2015)
# state number 10
fars_map_state(10, 2015)
```

We can also calculate observations for every month and year by using `fars_summarize_years` function. 

```{r aggr}
setwd(file_path)
fars_summarize_years(2013:2015)
```


Voila!
